### 2021-10-17 test/lambdapure/compile/bench/speedup-rgn.tex
add speedup plotting code

\definecolor{color0}{rgb}{0.847058823529412,0.105882352941176,0.376470588235294}

\begin{axis}[
legend cell align={left},
legend columns=100,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, at={(1,1.3)}, draw=none},
tick align=outside,
tick pos=left,
x grid style={white!69.0196078431373!black},
xmin=-0.57, xmax=5.37,
xtick style={color=black},
xtick={0,1,2,3,4,5},
xticklabel style={rotate=15.0},
xticklabels={binarytrees-int,binarytrees,filter,qsort,rbmap\_checkpoint,unionfind},
y grid style={white!69.0196078431373!black},
ylabel style={rotate=-90.0},
ylabel={Speedup over no simplifier},
ymin=0, ymax=1.071,
ytick style={color=black}
]
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.1,0.99);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0}
\addlegendentry{λpure over none}

\draw[draw=none,fill=color0] (axis cs:0.7,0) rectangle (axis cs:0.9,1);
\draw[draw=none,fill=color0] (axis cs:1.7,0) rectangle (axis cs:1.9,1.02);
\draw[draw=none,fill=color0] (axis cs:2.7,0) rectangle (axis cs:2.9,0.98);
\draw[draw=none,fill=color0] (axis cs:3.7,0) rectangle (axis cs:3.9,0.98);
\draw[draw=none,fill=color0] (axis cs:4.7,0) rectangle (axis cs:4.9,0.97);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:-0.1,0) rectangle (axis cs:0.1,0.99);
\addlegendimage{ybar,ybar legend,draw=none,fill=white!61.9607843137255!black}
\addlegendentry{rgn over none}

\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:0.9,0) rectangle (axis cs:1.1,1);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:1.9,0) rectangle (axis cs:2.1,1.02);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:2.9,0) rectangle (axis cs:3.1,1);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:3.9,0) rectangle (axis cs:4.1,1);
\draw[draw=none,fill=white!61.9607843137255!black] (axis cs:4.9,0) rectangle (axis cs:5.1,1);
\draw (axis cs:-0.3,0.99) ++(0pt,1pt) node[
  scale=0.347,
  anchor=south,
  text=black,
  rotate=0.0
]{0.99};
\draw (axis cs:0.7,1) ++(0pt,1pt) node[
  scale=0.347,
  anchor=south,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:1.7,1.02) ++(0pt,1pt) node[
  scale=0.347,
  anchor=south,
  text=black,
  rotate=0.0
]{1.02};
\draw (axis cs:2.7,0.98) ++(0pt,1pt) node[
  scale=0.347,
  anchor=south,
  text=black,
  rotate=0.0
]{0.98};
\draw (axis cs:3.7,0.98) ++(0pt,1pt) node[
  scale=0.347,
  anchor=south,
  text=black,
  rotate=0.0
]{0.98};
\draw (axis cs:4.7,0.97) ++(0pt,1pt) node[
  scale=0.347,
  anchor=south,
  text=black,
  rotate=0.0
]{0.97};
\end{axis}

>>>>

\definecolor{color0}{rgb}{0.12156862745098,0.470588235294118,0.705882352941177}
\definecolor{color1}{rgb}{0.847058823529412,0.105882352941176,0.376470588235294}

\begin{axis}[
legend cell align={left},
legend columns=100,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, at={(1,1.3)}, draw=none},
tick align=outside,
tick pos=left,
x grid style={white!69.0196078431373!black},
xmin=-0.82, xmax=6.22,
xtick style={color=black},
xtick={0,1,2,3,4,5,6},
xticklabel style={rotate=15.0},
xticklabels={binarytrees-int,binarytrees,const\_fold,deriv,filter,rbmap\_checkpoint,unionfind},
y grid style={white!69.0196078431373!black},
ylabel style={rotate=-90.0},
ylabel={Runtimes},
ymin=0, ymax=1.491,
ytick style={color=black}
]
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.1,1);
\addlegendimage{ybar,ybar legend,draw=none,fill=color0}
\addlegendentry{λpure simplifier}

\draw[draw=none,fill=color0] (axis cs:0.7,0) rectangle (axis cs:0.9,1.01);
\draw[draw=none,fill=color0] (axis cs:1.7,0) rectangle (axis cs:1.9,1.3);
\draw[draw=none,fill=color0] (axis cs:2.7,0) rectangle (axis cs:2.9,0.78);
\draw[draw=none,fill=color0] (axis cs:3.7,0) rectangle (axis cs:3.9,0.97);
\draw[draw=none,fill=color0] (axis cs:4.7,0) rectangle (axis cs:4.9,1.15);
\draw[draw=none,fill=color0] (axis cs:5.7,0) rectangle (axis cs:5.9,0.85);
\draw[draw=none,fill=color1] (axis cs:-0.5,0) rectangle (axis cs:-0.3,1);
\addlegendimage{ybar,ybar legend,draw=none,fill=color1}
\addlegendentry{rgn simplifier}

\draw[draw=none,fill=color1] (axis cs:0.5,0) rectangle (axis cs:0.7,1);
\draw[draw=none,fill=color1] (axis cs:1.5,0) rectangle (axis cs:1.7,1.42);
\draw[draw=none,fill=color1] (axis cs:2.5,0) rectangle (axis cs:2.7,0.96);
\draw[draw=none,fill=color1] (axis cs:3.5,0) rectangle (axis cs:3.7,1.12);
\draw[draw=none,fill=color1] (axis cs:4.5,0) rectangle (axis cs:4.7,1.01);
\draw[draw=none,fill=color1] (axis cs:5.5,0) rectangle (axis cs:5.7,1);
\draw (axis cs:-0.3,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:0.7,1.01) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.01};
\draw (axis cs:1.7,1.3) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.3};
\draw (axis cs:2.7,0.78) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.78};
\draw (axis cs:3.7,0.97) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.97};
\draw (axis cs:4.7,1.15) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.15};
\draw (axis cs:5.7,0.85) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.85};
\draw (axis cs:-0.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:0.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\draw (axis cs:1.5,1.42) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.42};
\draw (axis cs:2.5,0.96) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{0.96};
\draw (axis cs:3.5,1.12) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.12};
\draw (axis cs:4.5,1.01) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.01};
\draw (axis cs:5.5,1) ++(0pt,5pt) node[
  scale=0.2895,
  anchor=north west,
  text=black,
  rotate=0.0
]{1.0};
\end{axis}
